\pagenumbering{gobble}
%-----------------------Contributions------------------------------------------------------

\section*{Contributions}
\addcontentsline{toc}{chapter}{\numberline{}Contributions}
\begin{enumerate}
\item Number of DCRM signatures from the field are analyzed and conclusions are drawn which will be useful in reading the DCRM signature
\item Developed an algorithm to determine the contact condition from DCRM signature that suggests the availability of CB for future switching operation
\item Identified a program to determine the health of CB during performance
\item Short circuit capability of CB under different fault conditions and its suitability for particular switching operation is determined
\item EMTP-RV model for Trnsient Recovery Voltage under faulty condition is
suggested
\end{enumerate}
\clearpage

%-------------------------References--------------------------------------------------------
\bibliographystyle{IEEEtran-mod}
\addcontentsline{toc}{chapter}{\numberline{}References}
\bibliography{References}
\clearpage

%-----------------------PUBLICATIONS---------------------------------------------------------
\section*{Publications}
\addcontentsline{toc}{chapter}{\numberline{}Publications}
\begin{enumerate}
\item \textquotedblleft An Overview of Dynamic Contact Resistance Measurement of HV Circuit Breakers\textquotedblright, J. Inst. Eng. (India) B, Vol. 97, No. 2, Jan. 2015, pp. 219-226.
\item \textquotedblleft Dynamic Contact Resistance Measurement on High Voltage Circuit Breaker\textquotedblright, International Journal of Engineering Research and Technology (IJERT), Vol. 3, Issue 1, January 2014, pp. 1292-1296.
\item \textquotedblleft Black ~Box ~Arc Modeling of High ~Voltage Circuit Breaker Using Matlab~/ ~Simulink\textquotedblright, International Journal of Electrical Engineering and Technology (IJEET), Vol. 3, Issue 1, January- June 2012, pp. 69-78. 
\end{enumerate}
\clearpage

%-----------------------Annexure A------------------------------------------------------

\chapter*{Annexure A}
\addcontentsline{toc}{chapter}{\numberline{}Annexure A}
\lstinputlisting{filename.java}
\clearpage

%-----------------------ACKNOWLEDGEMENT------------------------------------------------------

\begin{center}
\large \textbf{ACKNOWLEDGEMENT}
\addcontentsline{toc}{chapter}{\numberline{}Acknowledgement}
\end{center}

\setlength{\parskip}{1em}
\justify \normalsize I take this opportunity to thank my guide Dr. W. Z. Gandhare, Director, G.S.Moze College of Engineering, Pune for his valuable guidance and constant motivation during the research work. I wish to thank Internal Monitoring Committee Members Dr. A. S. Bhalchandra, Dr. M. G. Shaikh and Dr. A. G. Thosar, Head of Electrical Engineering Department, Government College of Engineering, Aurangabad for their valuable support, suggestions and extending all the facilities for completion of this research work. I am thankful to Dr. P.B. Murnal for permitting to carry out the research work. Many thanks to my colleagues at the institute for their help and support.

I owe special thanks to the authority of Crompton Greaves, Nashik for permitting to conduct the experimentation and measurements. Also I greatly acknowledge the authorities of PGCIL and MSETCL for the technical support and permission to visit the substation and carry out the testing.

Last but not least, I express my deepest love to my family with all my heart for patience and unfailing support through the research work.

\setlength{\parskip}{0em}
\vspace{2cm}
\begin{flushright}
\textbf{Anita Arun Bhole}
\end{flushright}
\clearpage